### 2018-10-08 mmm-minorcycle-ska.tex
SKA version of Distribution memo

\usepackage[sans]{tcc_doc} % SDP style file
\usepackage[english]{babel}
\usepackage{amssymb,amsmath} % for the math symbols
\usepackage{mdwlist}
\usepackage{geometry}
\usepackage{marginnote}
\usepackage{datetime}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{mathtools}
\usepackage{hhtensor}
\usepackage{color}
\usepackage{txfonts}
\usepackage{enumitem}
\usepackage{minted}
\usepackage{tcolorbox}
\usepackage{float}

@@

% Enter here some information needed to fill in the template Title to appear
% on the front pages (will be filled in via the \sdpfrontpage command)
\newcommand{\bigdoctitle}{Distribution of the Rau-Cornwell MSMFS algorithm \xspace}
% Title to go in the "Document Status Sheet" Document number
\newcommand{\docnr}{TCC-CASS-001\xspace}
% Context
\newcommand{\context}{(ASKAPsoft)}
% Revision
\newcommand{\revision}{0.9\xspace}
% Author(s)
\newcommand{\docauthor}{T.J.\ Cornwell\xspace}
% Lead author (goes in the footer)
\newcommand{\leadauthor}{T.J.\ Cornwell\xspace}
% Release date (YYYY-MM-DD)
\newcommand{\docudate}{\today\ \currenttime}
% Document classification
\newcommand{\classification}{Unrestricted}
% Status of the document (draft/final/etc.)
\newcommand{\docstatus}{For release\xspace}

@@

% Table with version numbers
\newcommand{\versiontable}{
  \begin{tabularx}{\textwidth}{|X|X|X|X|}
    \hline
    \bf{Version} & {\bf Date of issue} & {\bf Prepared by} & {\bf Comments}\\
    \hline
    0.9 & 30/04/2018 & T.J. Cornwell & Initial version \\
    \hline
    1.0 & 18/06/2018 & T.J. Cornwell & Corrections from Mitch \\
    \hline
  \end{tabularx}
}

%%%%%%%%%%%%% END OF USER SETTINGS %%%%%%%%%%%%%%%%%%%

% Table with signatures
\newcommand{\signaturetable}[3]{
  \begin{tabularx}{\textwidth}{|X|X|X|}
    \hline
    Name & Designation & Affilitation\\
    \hline
    {#1} & {#2} & {#3}\\
    \hline
    Signature \& Date: & & \\
    & & \\
    & & \\
    \hline
  \end{tabularx}
}

% Table with affiliations
\newcommand{\organisationtable}{
  \begin{center}
    \sffamily{\bf ORGANISATION DETAILS}\end{center}
  \begin{table}[htb]
    \centering
    \begin{tabular}[htb]{|l|l|}
      \hline
      Name & Tim Cornwell Consulting\\
      \hline
    \end{tabular}
  \end{table}
}

@@

% load automatic pages
\tccfrontpage

@@

% Add here the abbreviations used in your document
\sdplistofabbreviations
\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
    \item[ASKAP] Australian Square Kilometer Array Pathfinder\vspace{-0.2cm}
    \item[ARL] Algorithm Reference Library\vspace{-0.2cm}
    \item[FFT] Fast Fourier Transform\vspace{-0.2cm}
    \item[FoV] Field of View\vspace{-0.2cm}
    \item[MS-MFS] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[MAM] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[PSF] Point Spread Function \vspace{-0.2cm}
    \item[SDP] Scientific Data Processor\vspace{-0.2cm}
    \item[SKA] Square Kilometre Array\vspace{-0.2cm}
%    \item[] \vspace{-0.2cm}
\end{basedescript}

@@

\sdplistoftables

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/ASKAP_sim_restored.png}
  \caption{Test field imaged with the MSMFS, major/minor cycle algorithm in the ARL. The fit is to the first five Taylor terms (i.e. quintic). 16 facets on each axis were used, with overlap 16 pixels.}
  \label{fig:ASKAP_sim_restored}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/ASKAP_sim_residual.png}
  \caption{Residual for test field imaged with the MSMFS, major/minor cycle algorithm in the ARL. The fit is to the first five Taylor terms (i.e. quintic polynomial). 16 facets on each axis were used, with overlap 16 pixels.}
  \label{fig:ASKAP_sim_residual}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/error_versus_support.png}
  \caption{Fractional discrepancy as a function of PSF support. This shows a parallel 2048 by 2048 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each. The discrepancy is the difference between the image processed with PSF support and the image processed with PSF support set to cover the entire image.}
  \label{fig:error_vs_support}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/error_versus_support_ci.png}
  \caption{Fractional discrepancy as a function of PSF support after five major cycles. This shows a parallel 2048 by 2048 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each. The discrepancy is the difference between the image processed with PSF support and the image processed with PSF support set to cover the entire image.}
  \label{fig:error_vs_support_ci}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/time_versus_support}
  \caption{Processing time (seconds) as a function of PSF support. This shows  a parallel 1024 by 1024 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each.}
  \label{fig:time_vs_support}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_No_primary_beam_ASKAP_2km_2048.png}
  \caption{Integrated sub-image flux versus rank, for realistic image (constructed from S3-SEX) without a primary beam applied. Scales are [0, 3, 10], and the overlap is 16 pixels. The slope for all curves is mainly due to the statistics of image which is derived from radio source LogN/LogS relationship. This shows the complete absence of strong scaling i.e. adding more processors does not bring commensurate improvements in performance.}
  \label{fig:fluxes_without_pb}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_with_pb_ASKAP_2km.png}
  \caption{Integrated sub-image flux versus rank, for realistic image (constructed from S3-SEX) with a primary beam applied. Scales are [0, 3, 10], and the overlap is 16 pixels. Compared to figure \ref{fig:fluxes_without_pb}, the primary beam application shifts the high rank sub-images lower in flux. The scaling has improved slightly.}
  \label{fig:fluxes_with_pb}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_clipped_image_ASKAP_2km.png}
  \caption{Integrated sub-image flux versus rank for various numbers of sub-images, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 100uJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels.} 
  \label{fig:fractions_clipped_image}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/aggregate_scaling_single_ASKAP_beam_ASKAP_2km_2048.png}
  \caption{Aggregate scaling curve for 2km ASKAP configuration on multiple major cycles. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels. The image size is 2048 by 2048 pixels. The scaling of work with numbers of sub-images (i.e. independent processors) is much closer to flat.}
  \label{fig:aggregate_scaling_2km}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/aggregate_scaling_single_ASKAP_beam_ASKAP_6km_6144.png}
  \caption{Aggregate predicted scaling curve for 6km configuration. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10, 30], and the overlap is 48 pixels. The image size is 6144 by 6144 pixels.}
  \label{fig:aggregate_scaling_6km}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/full_askap_pb_4096.png}
  \caption{Full ASKAP primary formed by summing PAF beams in quadrature. The image size is 4096 by 4096 pixels.}
  \label{fig:full_askap_pb}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/full_askap_aggregate_scaling_ASKAP_2km_4096.png}
  \caption{Aggregate scaling curve for 2km ASKAP configuration using the full mosaic primary beam. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels. The image size is 4096 by 4096 pixels.}
  \label{fig:full_askap_aggregate_scaling_2km}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/number_active_Single_ASKAP_beam_ASKAP_2km_2048.png}
  \caption{Number of active ranks vs major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam.}
  \label{fig:number_active_ASKAP_2km}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/culm_time_per_cycle.png}
  \caption{Cumulative Measured time taken for the clean of each sub-image vs sub-image rank for each major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam. The work increases steadily with cycle. Note that there is a stopping problem that can consume extra time, as well as the costs of a major cycle.}
  \label{fig:culm_time_vs_cycle}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{./pngs/time_versus_rank.png}
  \caption{Measured time taken for the clean of each sub-image vs sub-image rank for each major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam. The work increases steadily with cycle. Note that there is a stopping problem that can consume extra time, as well as the costs of a major cycle.}
  \label{fig:time_vs_rank}
\end{figure}

@@

\pagebreak
\section{Work plan}

The work plan to bring the Sub-image \MAM\ to ASKAPsoft. is straightforward. The steps required are:

\begin{itemize}
	\item Develop sub-image scatter/gather in ASKAPsoft.
	\item Develop master/worker version of scatter/gather
	\item Deploy in cdeconvolver as a test harness
	\item Perform scaling tests and adjust as necessary
	\item Deploy in cimager
	\item Check for strong scaling
	\item Run on simulated and real ASKAP and SKA data
	\item Investigate scaling to SKA
	\item Write report
\end{itemize}

As part of this work, the stopping problem should be pursued further since this is leading to substantial overhead in unnecessary major cycles.

Access to ASKAP computing facilities will be necessary.

\pagebreak
\section{Conclusions}

@@

>>>>

\usepackage[sans]{sdp_doc} % SDP style file
\usepackage[english]{babel}
\usepackage{amssymb,amsmath} % for the math symbols
\usepackage{mdwlist}
\usepackage{geometry}
\usepackage{marginnote}
\usepackage{datetime}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{mathtools}
\usepackage{hhtensor}
\usepackage{color}
\usepackage{txfonts}
\usepackage{enumitem}
\usepackage{minted}
\usepackage{tcolorbox}
\usepackage{float}

@@

% Enter here some information needed to fill in the template Title to appear
% on the front pages (will be filled in via the \sdpfrontpage command)
\newcommand{\bigdoctitle}{SKA Memo ???: Distribution of the Rau-Cornwell MSMFS algorithm \xspace}
% Title to go in the "Document Status Sheet" Document number
\newcommand{\doctype}{Memo}
\newcommand{\docnr}{SKA Memo ???\xspace}
% Context
\newcommand{\context}{(SDP.PIP)}
% Revision
\newcommand{\revision}{0.9\xspace}
% Author(s)
\newcommand{\docauthor}{T.J.\ Cornwell\xspace}
% Lead author (goes in the footer)
\newcommand{\leadauthorname}{T.J.\ Cornwell\xspace}
\newcommand{\leadauthordesignation}{Author}
\newcommand{\leadauthoraffiliation}{TCC}
\newcommand{\ownername}{T.J.\ Cornwell\xspace}
\newcommand{\footerauthor}{T.J.\ Cornwell\xspace}
\newcommand{\ownerdesignation}{Author}
\newcommand{\owneraffiliation}{TCC}
\newcommand{\approvername}{P.\ Alexander\xspace}
\newcommand{\approverdesignation}{SDP Lead}
\newcommand{\approveraffiliation}{U.Cam.}
\newcommand{\releasername}{P.\ Alexander\xspace}
\newcommand{\releaserdesignation}{SDP Lead}
\newcommand{\releaseraffiliation}{U.Cam.}
% Release date (YYYY-MM-DD)
\newcommand{\docudate}{\today\ \currenttime}
% Document classification
\newcommand{\classification}{Unrestricted}
% Status of the document (draft/final/etc.)
\newcommand{\docstatus}{Draft\xspace}

@@

\newcommand{\secondsigname}{T.J. Cornwell}
\newcommand{\secondsigdesignation}{Lead Consultant}
\newcommand{\secondsigaffiliation}{TCC}

% Table with version numbers
\newcommand{\versiontable}{
  \begin{tabularx}{\textwidth}{|X|X|X|X|}
    \hline
    \bf{Version} & {\bf Date of issue} & {\bf Prepared by} & {\bf Comments}\\
    \hline
    0.9 & 08/10/2018 & T.J. Cornwell & Ready for review \\
    1.0 & ?? & T.J. Cornwell & To be signed \\
    \hline
  \end{tabularx}
}
%%%%%%%%%%%%% END OF USER SETTINGS %%%%%%%%%%%%%%%%%%%

% Table with signatures
\newcommand{\signaturetable}[4]{
  \begin{tabularx}{\textwidth}{|X|X|X|}
    \hline
    {#1} & Designation & Affiliation\\
    \hline
    {#2} & {#3} & {#4}\\
    \hline
    Signature \& Date: & & \\
    & & \\
    & & \\
    \hline
  \end{tabularx}
}

% Table with the SDP details
\clearpage
\newcommand{\organisationtable}{
  \begin{center}
    \sffamily{\bf ORGANISATION DETAILS}\end{center}
  \begin{table}[htbp]
    \centering
    \begin{tabular}[htbp]{|c|l|}
      \hline
      Name & Science Data Processor Consortium\\
      \hline
      Address & Astrophysics\\
      & Cavendish Laboratory\\
      & JJ Thomson Avenue\\
      & Cambridge CB3 0HE\\
      \hline
      Website & http://ska-sdp.org\\
      \hline
      Email & ska-sdp-pa@mrao.cam.ac.uk\\
      \hline
    \end{tabular}
  \end{table}
}

@@

% load automatic pages
\sdpfrontpage

@@

% Add here the abbreviations used in your document
\sdplistofabbreviations
\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
    \item[ASKAP] Australian Square Kilometer Array Pathfinder\vspace{-0.2cm}
    \item[ARL] Algorithm Reference Library\vspace{-0.2cm}
    \item[FFT] Fast Fourier Transform\vspace{-0.2cm}
    \item[FoV] Field of View\vspace{-0.2cm}
    \item[MS-MFS] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[M\&M] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[PSF] Point Spread Function \vspace{-0.2cm}
    \item[SDP] Scientific Data Processor\vspace{-0.2cm}
    \item[SKA] Square Kilometre Array\vspace{-0.2cm}
%    \item[] \vspace{-0.2cm}
\end{basedescript}

@@

%\sdplistoftables

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/ASKAP_sim_restored.png}
  \caption{Test field imaged with the MSMFS, major/minor cycle algorithm in the ARL. The fit is to the first five Taylor terms (i.e. quintic). 16 facets on each axis were used, with overlap 16 pixels.}
  \label{fig:ASKAP_sim_restored}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/ASKAP_sim_residual.png}
  \caption{Residual for test field imaged with the MSMFS, major/minor cycle algorithm in the ARL. The fit is to the first five Taylor terms (i.e. quintic polynomial). 16 facets on each axis were used, with overlap 16 pixels.}
  \label{fig:ASKAP_sim_residual}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/error_versus_support.png}
  \caption{Fractional discrepancy as a function of PSF support. This shows a parallel 2048 by 2048 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each. The discrepancy is the difference between the image processed with PSF support and the image processed with PSF support set to cover the entire image.}
  \label{fig:error_vs_support}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/error_versus_support_ci.png}
  \caption{Fractional discrepancy as a function of PSF support after five major cycles. This shows a parallel 2048 by 2048 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each. The discrepancy is the difference between the image processed with PSF support and the image processed with PSF support set to cover the entire image.}
  \label{fig:error_vs_support_ci}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/time_versus_support}
  \caption{Processing time (seconds) as a function of PSF support. This shows  a parallel 1024 by 1024 pixel, 3 term \MAM\ clean in ARL. The computer was running 4 Dask workers with 32GB each.}
  \label{fig:time_vs_support}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_No_primary_beam_ASKAP_2km_2048.png}
  \caption{Integrated sub-image flux versus rank, for realistic image (constructed from S3-SEX) without a primary beam applied. Scales are [0, 3, 10], and the overlap is 16 pixels. The slope for all curves is mainly due to the statistics of image which is derived from radio source LogN/LogS relationship. This shows the complete absence of strong scaling i.e. adding more processors does not bring commensurate improvements in performance.}
  \label{fig:fluxes_without_pb}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_with_pb_ASKAP_2km.png}
  \caption{Integrated sub-image flux versus rank, for realistic image (constructed from S3-SEX) with a primary beam applied. Scales are [0, 3, 10], and the overlap is 16 pixels. Compared to figure \ref{fig:fluxes_without_pb}, the primary beam application shifts the high rank sub-images lower in flux. The scaling has improved slightly.}
  \label{fig:fluxes_with_pb}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/fluxes_clipped_image_ASKAP_2km.png}
  \caption{Integrated sub-image flux versus rank for various numbers of sub-images, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 100uJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels.} 
  \label{fig:fractions_clipped_image}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/aggregate_scaling_single_ASKAP_beam_ASKAP_2km_2048.png}
  \caption{Aggregate scaling curve for 2km ASKAP configuration on multiple major cycles. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels. The image size is 2048 by 2048 pixels. The scaling of work with numbers of sub-images (i.e. independent processors) is much closer to flat.}
  \label{fig:aggregate_scaling_2km}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/aggregate_scaling_single_ASKAP_beam_ASKAP_6km_6144.png}
  \caption{Aggregate predicted scaling curve for 6km configuration. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10, 30], and the overlap is 48 pixels. The image size is 6144 by 6144 pixels.}
  \label{fig:aggregate_scaling_6km}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/full_askap_pb_4096.png}
  \caption{Full ASKAP primary formed by summing PAF beams in quadrature. The image size is 4096 by 4096 pixels.}
  \label{fig:full_askap_pb}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/full_askap_aggregate_scaling_ASKAP_2km_4096.png}
  \caption{Aggregate scaling curve for 2km ASKAP configuration using the full mosaic primary beam. Fraction of flux versus rank for various numbers of facets, for realistic image (constructed from S3-SEX) with a primary beam applied and then clipped at 1mJy/beam. Scales are [0, 3, 10], and the overlap is 16 pixels. The image size is 4096 by 4096 pixels.}
  \label{fig:full_askap_aggregate_scaling_2km}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/number_active_Single_ASKAP_beam_ASKAP_2km_2048.png}
  \caption{Number of active ranks vs major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam.}
  \label{fig:number_active_ASKAP_2km}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/culm_time_per_cycle.png}
  \caption{Cumulative Measured time taken for the clean of each sub-image vs sub-image rank for each major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam. The work increases steadily with cycle. Note that there is a stopping problem that can consume extra time, as well as the costs of a major cycle.}
  \label{fig:culm_time_vs_cycle}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./pngs/time_versus_rank.png}
  \caption{Measured time taken for the clean of each sub-image vs sub-image rank for each major/minor cycle, for 2km ASKAP configuration using the single primary beam. The threshold for each cycle starts at $\sqrt{0.1}$ Jy/beam and proceeds in geometric progression to 0.1 mJy/beam. The work increases steadily with cycle. Note that there is a stopping problem that can consume extra time, as well as the costs of a major cycle.}
  \label{fig:time_vs_rank}
\end{figure}

@@

%\pagebreak
%\section{Work plan}
%
%The work plan to bring the Sub-image \MAM\ to ASKAPsoft is straightforward. The steps required are:
%
%\begin{itemize}
%	\item Develop sub-image scatter/gather in ASKAPsoft.
%	\item Develop master/worker version of scatter/gather
%	\item Deploy in cdeconvolver as a test harness
%	\item Perform scaling tests and adjust as necessary
%	\item Deploy in cimager
%	\item Check for strong scaling
%	\item Run on simulated and real ASKAP and SKA data
%	\item Investigate scaling to SKA
%	\item Write report
%\end{itemize}
%
%As part of this work, the stopping problem should be pursued further since this is leading to substantial overhead in unnecessary major cycles.
%
%Access to ASKAP computing facilities will be necessary. 
%
\pagebreak
\section{Conclusions}

@@

\pagebreak
\section{Acknowledgements}

I thank Daniell Mitchell for comments. This work ws supported by CSIRO CASS.
